Artin Group Presentations Arising from Cluster Algebras

### 2014-07-30 Paper.tex
"Additional edits to t notation aaron"

\indent Given a diagram $\Gamma$, Barot and Marsh define for $i, j \in \V$,
\begin{displaymath}
\label{mij_defn}
m_{ij} = \begin{cases} 2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
3 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 1;\\
4 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 2;\\
6 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 3.\\
\end{cases}
\end{displaymath}

@@

\begin{defn} \label{grp def}

Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin group as follows. The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
\item[(T2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
\begin{enumerate}
\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
we include the relation
\begin{align*}
s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} s_{a}^{-1}\dots s_{a-2}^{-1}s_{a-1}^{-1}s_{a-2}s_{a-3} \dots s_{a+1} = e
\end{align*}
where subscripts are taken $\pmod d.$ We will denote this relation by $t(a,a+1) = e$.
\end{itemize}
\end{defn}

>>>>

\begin{note}
\label{defn:mij}
\indent Given a diagram $\Gamma$, Barot and Marsh define for $i, j \in \V$,
\begin{displaymath}
m_{ij} = \begin{cases} 2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
3 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 1;\\
4 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 2;\\
6 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 3.\\
\end{cases}
\end{displaymath}	
\end{note}

@@

Finally, we are ready to define the Artin group we associate to a diagram of finite type. First, we shall need a tiny bit more notation.

\begin{note}
Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$ Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1}) p(i_a,i_{a+1})^{-1} s_{i_a}^{-1}.$$
\end{note}

\begin{defn} \label{grp def}
The {\it associated Artin group} to a diagram $\Gamma$ of finite type, denoted $A_\Gamma,$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
\item[(T2)] With $m_{ij}$ as defined in Definition ~\ref{defn:mij}, for all $i \neq j,$ we add the relations
$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally, one of the following two conditions hold,
\begin{enumerate}
\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
then, we include the relation
$t(i_0,i_1) = e.$
\end{itemize}
\end{defn}
